---
title: "Model 1A Sensitivity Run 001"
format:
  html:
    toc: true
    code-fold: true
params:
  scenario_id: "001"
  scenario_label: "Baseline"
  max_time: 365
  dt: 0.5
execute:
  echo: true
  warning: false
  message: false
---

```{r}
source("Model1A_Parameters.R")
source("Model1A_Functions.R")
```

```{r}
pars <- build_model1a_parameters(
  scenario_id = params$scenario_id,
  scenario_label = params$scenario_label,
  max_time = params$max_time,
  dt = params$dt
)

output_root <- file.path("..", "Outputs")
scenario_tag <- paste0("Model1A_Run_Sens_", params$scenario_id)
output_dir <- file.path(output_root, scenario_tag)
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)

times <- make_model1a_times(pars$max_time, pars$dt)
out <- ode(
  y = pars$initial_state,
  times = times,
  func = model1a_ode,
  parms = pars,
  method = "lsoda"
)

out <- as.data.frame(out)
out <- calculate_model1a_derived_outputs(out)
stab_row <- find_model1a_stabilisation(out, tol = pars$stabilisation_tol, window = pars$stabilisation_window)
stab_summary <- summarise_model1a_stabilisation(out, stab_row)
files <- save_model1a_outputs(out, stab_row, output_dir, scenario_tag)
```

## Scenario details

- Scenario ID: `r params$scenario_id`
- Scenario label: `r params$scenario_label`
- Time step: `r params$dt` days
- Horizon: `r params$max_time` days

## State trajectories by time step

```{r}
knitr::kable(
  out[, c("time", "S", "C", "I", "X", "E")],
  digits = 4,
  caption = "Numbers in each state at each time step"
)
```

The full state trajectory table is also saved to:

`r normalizePath(files$state_file)`

## Cumulative outcomes

```{r}
knitr::kable(
  out[, c("time", "CumCases", "CumIdentified", "CumFalseNeg", "CumDischC", "CumDischI", "CumXDays", "CumDeaths", "CumCI", "CumAdmI", "CumXS", "CumXI", "CumXDisch")],
  digits = 4,
  caption = "Cumulative totals across the simulation"
)
```

The full cumulative table is also saved to:

`r normalizePath(files$cum_file)`

## Values at model stabilisation

Stabilisation is taken as the first time point where the absolute change in all core states remains below the tolerance for the configured window.

```{r}
knitr::kable(stab_summary, digits = 4, caption = "State values and outcomes at model stabilisation")
```

The stabilisation summary is also saved to:

`r normalizePath(files$stab_file)`

## Plots

```{r}
knitr::include_graphics(files$plot_states_file)
knitr::include_graphics(files$plot_cum_file)
knitr::include_graphics(files$plot_outcomes_file)
```

## Outcome definitions used here

- Total cases = `CumCI + CumAdmI`
- Identified cases = `CumXS + CumXDisch`
- Missed cases = `Total cases - Identified cases`
- False negatives = `CumXI`
- Invasive infections not identified as suspected cases = `Missed cases - False negatives`
- Side-room use (patient-days) = cumulative area under `X`
